Energy and the CES production function

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Edits to sigma graph.

%++++++++++++++++++++++++++++++
\subsection{$\sigma$ graph} 
\label{sec:sigma_graph}
%++++++++++++++++++++++++++++++

<<sigma_graph>>=
sigma_graph_data <- filter(AllCoeffs, model=="CES") %>% 
  select(Country, CSP, flavor, energy, nest, sigma_12, sigma_23, sigma_13, sigma_12_3, sigma_23_1, sigma_13_2)
# Change nest to a nicer-looking nest string
sigma_graph_data$nest <- plyr::mapvalues(sigma_graph_data$nest, 
                                         from=c("kl", "kle", "lek", "ekl"), 
                                         to=c("kl", "(kl)e", "(le)k", "(ek)l"))
# Now melt the data
sigma_graph_data <- melt(sigma_graph_data, 
                         measure.vars = c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"), 
                         value.name = "value", 
                         variable.name = "variable")
# Create labels
sigma_graph_data$label <- paste(sigma_graph_data$CSP, sigma_graph_data$flavor, 
                                sigma_graph_data$energy, sigma_graph_data$nest, 
                                sigma_graph_data$variable, sep=", ")
sigma_graph_data <- na.omit(sigma_graph_data)

# Make the plot
plot <- ggplot(sigma_graph_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
  geom_bar(stat="identity") + 
  xlab("") +
  # scale_x_discrete(limits=rev(order)) +
  ylab("") +
#   scale_y_continuous(breaks=c(0, 0.5, 1)) + 
  guides(fill=guide_legend(title=NULL)) +
  scale_fill_brewer(palette="OrRd") +
  coord_flip() + 
  xy_theme() +
  theme(axis.ticks.y = element_blank())
plot # for debugging
@

>>>>

%++++++++++++++++++++++++++++++
\subsection{$\sigma$ graphs} 
\label{sec:sigma_graphs}
%++++++++++++++++++++++++++++++

<<sigma_graph_function>>=

sigma_graph_function <- function(data){
  sigma_graph_data <- select(data, Country, CSP, flavor, energy, nest, 
                             sigma_12, sigma_23, sigma_13, 
                             sigma_12_3, sigma_23_1, sigma_13_2)
  # Change nest to a nicer-looking nest string
  sigma_graph_data$nest <- plyr::mapvalues(sigma_graph_data$nest, 
                                           from=c("kl", "kle", "lek", "ekl"), 
                                           to=c("kl", "(kl)e", "(le)k", "(ek)l"))
  # Now melt the data
  sigma_graph_data <- melt(sigma_graph_data, 
                           measure.vars = c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"), 
                           value.name = "value", 
                           variable.name = "variable")
  # Create a nicer-looking sigma
#   sigma_graph_data$variable <- plyr::mapvalues(sigma_graph_data$variable,
#                                                from=c("sigma_12", 
#                                                       "sigma_23",
#                                                       "sigma_13",
#                                                       "sigma_12_3",
#                                                       "sigma_23_1",
#                                                       "sigma_13_2"),
#                                                to=c("expression(sigma[kl])", 
#                                                     "expression(sigma[le])",
#                                                     "expression(sigma[ek])",
#                                                     'expression(sigma["(kl)"*e])',
#                                                     'expression(sigma["(le)"*k])',
#                                                     'expression(sigma["(ek)"*l])'))
  # Create labels
  sigma_graph_data$label <- paste(sigma_graph_data$CSP, sigma_graph_data$flavor, 
                                  sigma_graph_data$energy, sigma_graph_data$nest, 
                                  sigma_graph_data$variable, sep=", ")
  sigma_graph_data <- na.omit(sigma_graph_data)

  # Make the plot
  plot <- ggplot(sigma_graph_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
    geom_bar(stat="identity") + 
    xlab("") +
    # scale_x_discrete(limits=rev(order)) +
    scale_x_discrete(labels=sigma_graph_data$label) +
    geom_hline(aes(yintercept = 1), colour="gray50", size=0.1) +
    ylab("") +
    # coord_trans(y="sigma") +
    scale_y_continuous(limits=c(0, 10), breaks=c(0, 1.0, 10)) +
    guides(fill=guide_legend(title=NULL)) +
    scale_fill_brewer(palette="OrRd") +
#     scale_fill_brewer(palette="OrRd",
#                       labels=c(expression(sigma[kl]), 
#                                expression(sigma[le]), 
#                                expression(sigma[ek]),
#                                expression(sigma["(kl)e"]),
#                                expression(sigma["(le)k"]),
#                                expression(sigma["(ek)l"]))) +
    coord_flip() + 
    xy_theme() +
    theme(axis.ticks.y = element_blank())
  return(plot)
}
@

<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.">>=
sigma_graph_function(filter(AllCoeffs, model=="CES", Country=="PT"))
@

<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.">>=
sigma_graph_function(filter(AllCoeffs, model=="CES", Country=="UK"))
@
